My title

### 2024-09-15 outputs/paper/paper.qmd
Second edition of results

We dropeed the only missing row corresponding to july-2024. We selected our columns of interest, namely, gender: ('male', 'female', 'transgender_non_binary_or_two_spirit'), total number of homeless people every month ('actively_homeless'), as well as refugee and chronic status in polulation column. In addition, we grouped age group by whether they are suitable for work (age under 24 for early career stage, age25-44 for working age and age above 45 for pre-retirement and retirement age). Finally, we replace the month data by averaged quatered data for better analysis and visualization of a prelonged time period. The cleaned data could be seen in @tbl-cleandata.

@@

First, we plot the bar graph of over all trend of homeless people over the pass of the time. In @fig-overall, we observe an slightly increase of total number of homeless people from first quarter 2018 to second quarter of 2024. There is a decrease of homeless population in late 2020-early 2021, but increased quickly after that.

@@

## Gender trend
Next, we investigate the trend of gender proportion. We plot the proportion of male, female, and Other genders against time in @fig-gender. Even thought there is some flatuations of the proportion of these three gender types, the overall trend is quite stable. The male proportion is around 60% while female proportion around 40% and others around 1%.

## Chronic trend
@fig-Chronic shows the trend of the proportion of chronic population among all of homeless people over the quarters of a year. Here, according to @chronic, chronic homeless refers to, "People who meet one of the two following criteria, as per the federal definition of chronic homelessness. The person has recorded a minimum of 180 overnight stay in the past year (365 days); or the person has recurrent overnight stays over the past three years with a cumulative duration of at least 546 nights." We can see form the graph that the proportion in chronic homeless increased a lot, from less than 35% in first quarter of 2018 to more than 65% in the second quarter of 2024. 
```{r}
#| label: fig-Chronic
#| echo: false
#| fig-cap: "Proportion of Chronic population to Active Population by Quarter"

@@

# Create a bar graph
ggplot(plot_data, aes(x = Quarter, y = Proportion)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Quarters", y = "Proportion of Chronic to Active Population") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
## Age trend
@fig-WorkingAge shows the trend of the proportion of different working age statuses among the actively homeless population over the quarters of a year. Here, the working age statuses are categorized into three groups: Early Career Stage, Working Age, and Pre-Retirement and Retirement Age.Even thought the trend is not huge, We can see from the graph that the proportion of the Early Career Stage population  as well as pre-retire and retire have decreased (from 29% and 33% separately in first quarter of 2018 to 25% and 28% in second quarter in 2024). On the other hand, working age proportion increased to 47% in 2024Q2 from 37% in 2018Q1. 
```{r}
#| label: fig-WorkingAge
#| echo: false
#| fig-cap: "Proportion of working age population to Active Population by Quarter"

@@

## Refugee trend
@fig-refugee shows the trend of the proportion of refugees among the actively homeless population over the quarters of a year. We observe a signifiacant decrease of the trend accompanyed by even more signifcant increase. 
```{r}
#| label: fig-refugee
#| echo: false
#| fig-cap: "Proportion of Chronic population to Active Population by Quarter"

>>>>

We dropped the only missing row corresponding to July 2024. We then selected our columns of interest, namely, the total number of homeless people every month **actively_homeless**, gender ratio: **male**, **female**, **transgender_non_binary_or_two_spirit**, as well as refugee and chronic status in column **population**. In addition, we categorize age groups by whether they are suitable for work: transform age under 24 for **early career stage**, age between 25 and 44 for **working age**, and age above 45 for **pre-retirement and retirement age**. Finally, we replace the monthly data with averaged quarterly data for better analysis and visualization of a prolonged period. A sample of cleaned data can be seen in @tbl-cleandata.

@@

First, we plot a bar graph to show the trend of the size of the entire homeless population of homeless people over the past time. In @fig-overall, we observe a slight increase in the total number of homeless people from the first quarter of 2018 to the second quarter of 2024, while in between there is a decrease of the homeless population in late 2020 to early 2021, followed by a rapid increase.

@@

## Gender trend
Next, we investigate the trend of gender ratio. We plot the proportion of male, female, and Other gender types against time in @fig-gender. Even though there is some fluctuation in the proportion of these three gender types, the overall trend is stable. The male proportion stays around 60% while the female proportion stays around 40% and others around 1%.

## Chronic trend
@fig-Chronic shows the trend of the proportion of chronic population among all homeless people over the quarters of each year. Here, according to [@chronic], chronic homelessness refers to "People who meet one of the two following criteria, as per the federal definition of chronic homelessness. The person has recorded a minimum of 180 overnight stays in the past year (365 days), or the person has recurrent overnight stays over the past three years with a cumulative duration of at least 546 nights." We can see from the graph that the proportion of chronic homeless increased a lot, from less than 35% in the first quarter of 2018 to more than 65% in the second quarter of 2024. 
```{r}
#| label: fig-Chronic
#| echo: false
#| fig-cap: "Proportion of Chronic population to Active Population by Quarter"

@@

# Create a bar graph
ggplot(plot_data, aes(x = Quarter, y = Proportion)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Quarters", y = "Proportion of Chronic to Active Population") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
## Age trend
@fig-WorkingAge displays the trend of the proportion of different working age statuses among the actively homeless population over the quarters of each year. Here, the working age statuses are categorized into three groups: Early Career Stage, Working Age, and Pre-Retirement and Retirement Age. Even though the trend is not dramatic, We can see from the graph that the proportion of the Early Career Stage population as well as pre-retire and retired has decreased (from 29% and 33% separately in the first quarter of 2018 to 25% and 28% in the second quarter in 2024). On the other hand, the working age proportion increased to 47% in 2024Q2 from 37% in 2018Q1. This indicates the growing population who are in the working age cannot afford their housing. 
```{r}
#| label: fig-WorkingAge
#| echo: false
#| fig-cap: "Proportion of working age population to Active Population by Quarter"

@@

## Refugee trend
@fig-refugee shows the trend of the proportion of refugees among the actively homeless population over the quarters of each year. We observe a significant decrease in the proportion of individuals with refugee status from 35% in 2019 to less than 20% in 2021. However, starting in the year 2022, the proportion surged to nearly 60% in the second quarter of 2024. 
```{r}
#| label: fig-refugee
#| echo: false
#| fig-cap: "Proportion of Chronic population to Active Population by Quarter"
